---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(naratext)
```

# naratext

<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
[![R-CMD-check](https://github.com/coolbutuseless/naratext/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/coolbutuseless/naratext/actions/workflows/R-CMD-check.yaml)
![](https://img.shields.io/badge/status-experimental-yellow.svg)
<!-- badges: end -->

`{naratext}` renders text to nativeRaster images in memory.

This relies of glyph rendering features in the `{grid}` package.


### What's in the box

* `nr_text()` to render text to in-memory nativeRaster images

### ToDo

* Reconcile the different font handling mechanisms between `textshaping` and 
  `grDevices::glyphFont()`
* Tightly crop the returned nativeRaster
* Return baseline offset from bottom of raster so that other compositors (e.g. `{nara}`)
  now how to place text correctly
* Move to textshaping's C interface?


## Installation from [GitHub](https://github.com/coolbutuseless/naratext)

Also requires installation of:

* CRAN packages: 
    * [`{textshaping}`](https://cran.r-project.org/package=textshaping) 
      to calculate positions of rendered glyph
    * [`{ragg}`](https://cran.r-project.org/package=ragg) as a graphics 
      device that allows direct capture of the output to an image in memory
      (and supports glyph rendering)
* GitHub packages
    * [`{nara}`](https://github.com/coolbutuseless/nara) for nativeRaster conversion

``` r
install.packages('remotes')
remotes::install_github('coolbutuseless/nara')
install.packages(c('textshaping', 'ragg'))

remotes::install_github('coolbutuseless/naratext')
```

## Example - full font rendering

```{r example, fig.height = 1.5}
library(grid)
library(nara)
library(naratext)

strings <- c('Ping', ' #RStats')
font_files <- c(
  system.file("fonts", "Montserrat", "static", "Montserrat-BoldItalic.ttf", package="grDevices"),
  system.file("fonts", "Montserrat", "static", "Montserrat-Medium.ttf"    , package="grDevices")
)
color <- c('red', 'blue')
txt <- nr_text(strings, font_files = font_files, color = color, scale = 10, background = 'lightblue')
dim(txt)
class(txt)
grid.raster(txt, interpolate = FALSE)
```

## Example - Bitmap font rendering

```{r fig.height = 1.5}
library(grid)
library(nara)
library(naratext)

font_file <- system.file("fonts/spleen/spleen-8x16.hex.gz", package = "bittermelon") 
font <- bittermelon::read_hex(font_file)
txt <- nr_text_bitmap("Ping #RStats", font = font, fill = 'lightblue')
grid::grid.newpage()
grid::grid.raster(txt, interpolate = FALSE)
```



