---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(naratext)
```

# naratext

<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
<!-- badges: end -->

`{naratext}` renders text to raster/nativeRaster images using:

* `{textshaping}` to figure out rendered glyph positions 
* `{ragg}` as a graphis device that allows direct capture of the output to a variable
  (rather than writing to file or screen)
* `grid::grid.glyph()` for rendering the glyphs in the calculated positions

## Installation

You can install from [GitHub](https://github.com/coolbutuseless/naratext) with:

``` r
# install.packages('remotes')
remotes::install_github('coolbutuseless/naratext')
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#' install.packages(c('textshaping', 'ragg'))
library(nara)
library(naratext)

strings <- c('Ping', ' #RStats')
font_files <- c(
  system.file("fonts", "Montserrat", "static", "Montserrat-BoldItalic.ttf", package="grDevices"),
  system.file("fonts", "Montserrat", "static", "Montserrat-Medium.ttf"    , package="grDevices")
)
color <- c('red', 'blue')
txt <- nr_text(strings, font_files = font_files, color = color)
plot(txt, T)
```




